Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-11 automatica/paper.tex
section 4

In this section we discuss two instantiations of CEGIS: the first,
na\"ive one, relies on an unfolding of the dynamics up to a
completeness threshold, while the second one is abstraction-based and
leverages abstraction refinement and acceleration to improve
scalability while retaining soundness.

@@

An overview of the algorithm for controller synthesis is given in Fig.~\ref{fig:CEGIS-precision-increment}.  
One important observation is that we verify and synthesize a controller over a finite number ($k$) of time steps.  
We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} 
for this controller, and verify correctness for $\overline{k}$ time steps. 
As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the closed-loop state-space model,  
ensuring that the boundaries are not violated for any other $k{>}\overline{k}$.

@@

Next, we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).

>>>>

In this section we discuss two instantiations of CEGIS: 
the first one,
named {\it multi-stage} approach, 
relies on an unfolding of the dynamics up to a completeness threshold; 
the second one is {\it abstraction-based}, 
and it leverages abstraction-refinement \note{ cit.} and acceleration \note{ref to relevant section} to improve scalability,  
while retaining soundness.

@@

An overview of the algorithm for controller synthesis is given in Figure~\ref{fig:CEGIS-precision-increment}.   
One important point is that we formally synthesize a controller over a finite number ($k$) of time steps.  
We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} for this controller, 
and verify the correct behaviour for $\overline{k}$ time steps. 
As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the dynamics of the closed-loop state-space model,  
ensuring that the safety boundaries are not violated for any other $k{>}\overline{k}$.

@@

Next, 
with reference to the CEGIS scheme in Figure~\ref{fig:CEGIS}, 
we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
